I don't know, are you sure we want to do this?\\ Sea level adaptation decisions under uncertainty

### 2016-11-21 submission/paper.tex
Added text about Bergen and Esbjerg in the introduction.

@@

\begin{figure}[!hbpt]
\begin{center}
\includegraphics[width=0.5\linewidth]{unc.pdf}
\caption{2050 Bergen sea level projections with uncertainty due to different sources for RCP 8.5. The black line is the median projection (with no uncertainty), while the grey histogram corresponds to the spread of the climate models, the red curve adds the uncertainty due to the relation between global temperature and global sea level, and the blue line that due to downscaling global sea level to Bergen. } 
\label{fig:unc}
\end{center}
\end{figure}

>>>>

The Norwegian city of Bergen is the capital of Hordaland County. The city center is located on Byfjorden, and is surrounded by mountains. It has the largest port in Norway, both in terms of freight and passengers. The historic harbor area, Bryggen, is the only Hanseatic trade center remaining in its original style, and has been declared a UNESCO World Heritage site (\url{http://whc.unesco.org/en/list/59}). Bryggen is regularly flooded at extreme tides, and it is feared that as sea levels rise, floods will become a major problem in other parts of Bergen as well \citep{bergenreport}.

Esbjerg, on the west coast of Jutland,  has the second largest harbour in Denmark. It can be subjected to substantial storm surges, which, in conjunction with heavy rainfall, can flood substantial parts of the town.

@@

\begin{figure}[!hbpt]
\begin{center}
\includegraphics[width=0.5\linewidth]{unc.pdf}
\caption{2050 Bergen sea level projections with uncertainty due to different sources for RCP 8.5. The black vertical line is the median projection (with no uncertainty), while the grey histogram corresponds to the spread of the climate models, the red curve adds the uncertainty due to the relation between global temperature and global sea level, and the blue line that due to downscaling global sea level to Bergen. } 
\label{fig:unc}
\end{center}
\end{figure}
